Parallel multi-objective optimization using co-evolutionary islands with overlapping search space

### 2017-01-10 hpmoon-coor.tex
Re-organizing introduction according @JJ 's proposed new order. Some of his comments STILL need to be adressed by me

%Introduction should start in the same way as the abstract. And
%starting with something that is not really applicable here, talking
%about general parallel evolutionary algorithms, is even worse.
% Right way (IMNSHO)
% 1. Multiobjective problems are
% 2. They usually require a good amount of computation → parallel
% distributed
% 3. One way to solve them is to use MOEAs _because_ they can be
% easily parallelized
% 4. But the easy paralellization is not necessarily efficient.
% 5. We have proposed the HPMOON (or whatever) technique to improve
% it. In paper (whatever) we proved that (whatever)
% 6. In this paper we will be proving whatever - JJ
Different approaches have been used to parallelize Evolutionary
Algorithms (EAs), as each individual can be considered as an
independent unit \citep{Alba13parallel}. Classic methods, such as the
global parallel EAs (Master-Slave), or the spatially structured
algorithms (Island model or Cellular EAs) have been applied
successfully in the past \citep{Folino03cellular,Alba02Parallelism}.
In the case of Multi-Objective Evolutionary Algorithms (MOEAs), these
approaches \citep{Luna15Survey} need to deal with a whole solution set
called Pareto Front (PF). This imply to use different distribution
and sharing mechanisms, as there exist a tension between the speedup
achievable from parallelization and the need to globally recombine the
results to accurately identify the PF
\citep{Branke04Parallelizingcone}.

The application of MOEAs to solve real-world problems have gained attention in the last years \citep{Luna15Survey,Mukhopadhyay14Survey,Chavez15MO,Hidalgo16residualstress}. These kind of problems requires a high number of variables, meaning that the EAs need to deal with large individuals and spent significant extra time for crossover, mutation and migration. Different authors have proposed methods to divide the decision space (the chromosome) to improve the performance and solution quality. In this aspect, the co-evolution model is a dimension-distributed model where a high-dimensional problem is divided into lower dimensional problems \citep{Gong15models,Tonda12cooperative}, and evolved separately. One example of application of this technique was described in \citep{Kimovski15Parallel}. The method presented in that works involves different workers that evolve sub-populations created and recombined by a master process, which performs different recombination alternatives from the parts returned by worker processes. A high dimensional problem was used to compare these
alternatives. In \citep{Dorronsoro13superlinear}, a distributed
coevolutionary island model was used.  Although in both papers
significant speedups were attained, only a low number of nodes were
employed (8). However, when the number of islands is increased, the division
of each section of the chromosome becomes smaller, and the scalability
may be affected by obtaining lower quality solutions in the same
amount of time.

@@

@@

%This is not state of the art. If it's not an EC journal, it should go
%to the introduction - JJ
Evolutionary algorithms (EAs) \citep{DBLP:series/ncs/EibenS15,DeJong2006} are bio-inspired meta-heuristics that can be effectively used to find nearly optimal solutions for optimization problems. Usually an EA starts by generating a set of random solutions, called \emph{population}, following a user-defined description. Then, it evaluates each candidate solution, called \emph{individual}, assigning it a \emph{fitness} value, that describes how good the individual is, with regards to the target problem. New solutions are then generated by the application of \emph{operators} that either mutate a single solution or recombine different existing solutions. After each iteration, called \emph{generation}, the least fit individuals are removed, and the process continues until a user-defined stop condition is met.

% Not EA either. It's an explanation of the techniques you are using,
% thus Intro - JJ
Multi-objective optimization problems (MOP) are those where several
objectives have to be simultaneously optimized
\citep{Mora13paretobased}. Solving a MOP implies maximize or minimize
a function composed of several cost functions (one per objective). In
these problems the aim is to obtain a set of solutions that are better
than the rest, considering all the objectives; this set is known as
the Pareto Front. The solutions in this set are {\em non-dominated},
that is, none is better than the others for all the objectives. MOEAs
are sub-set of EAs used to solve MOPs. One of the most well-known and
referenced MOEAs \citep{Dorronsoro13superlinear} is the {\em
  Non-dominated Sorting Genetic Algorithm} (NSGA-II)
\citep{Deb00NSGAII}. Classical genetic operators are applied to all
the individuals, and divided into different ranks (based on the
dominance) to be selected for the next generations.

>>>>

%Introduction should start in the same way as the abstract. And
%starting with something that is not really applicable here, talking
%about general parallel evolutionary algorithms, is even worse.
% Right way (IMNSHO)
% 1. Multiobjective problems are
% 2. They usually require a good amount of computation → parallel
% distributed
% 3. One way to solve them is to use MOEAs _because_ they can be
% easily parallelized
% 4. But the easy paralellization is not necessarily efficient.
% 5. We have proposed the HPMOON (or whatever) technique to improve
% it. In paper (whatever) we proved that (whatever)
% 6. In this paper we will be proving whatever - JJ FERGU: Addressing JJ order

%1. MOP ARE
Multi-objective optimization problems (MOP) are those where several
objectives have to be simultaneously optimized
\citep{Mora13paretobased}. Solving a MOP implies maximize or minimize
a function composed of several cost functions (one per objective). In
these problems the aim is to obtain a set of solutions that are better
than the rest, considering all the objectives; this set is known as
the Pareto Front (PF). The solutions in this set are {\em non-dominated},
that is, none is better than the others for all the objectives.

%2 COMPUTATION -> PARALLEL
These kind of problems require a high demand of computational time, and that is the reason why easily parallelizable methods to solve them have appeared \citep{Luna15Survey,Mukhopadhyay14Survey,Chavez15MO,Hidalgo16residualstress}. %FERGU: TODO reescribir esta frase tan basura

%3 ONE WAY IS TO USE MOEAS BECAUSE
One example of easily parallelizable algorithms to solve MOPs are the Multi-Objective Evolutionary Algorithms (MOEAs), a sub-set of Evolutionary algorithms (EAs). EAs \citep{DBLP:series/ncs/EibenS15DeJong2006} are bio-inspired meta-heuristics that can be effectively used to find nearly optimal solutions for optimization problems. Usually an EA starts by generating a set of random solutions, called \emph{population}, following a user-defined description. Then, it evaluates each candidate solution, called \emph{individual}, assigning it a \emph{fitness} value, that describes how good the individual is, with regards to the target problem. New solutions are then generated by the application of \emph{operators} that either mutate a single solution or recombine different existing solutions. After each iteration, called \emph{generation}, the least fit individuals are removed, and the process continues until a user-defined stop condition is met.

 One of the most well-known and referenced MOEAs \citep{Dorronsoro13superlinear} is the {\em
  Non-dominated Sorting Genetic Algorithm} (NSGA-II)
\citep{Deb00NSGAII}. Classical genetic operators are applied to all
the individuals, and divided into different ranks (based on the
dominance) to be selected for the next generations.

%4 BUT THE EASY PARALLELIZATION IS NOT NECESSARILY EFFICIENT

Different approaches have been used to parallelize EAs, as each individual can be considered as an
independent unit \citep{Alba13parallel}. Classic methods, such as the
global parallel EAs (Master-Slave), or the spatially structured
algorithms (Island model or Cellular EAs) have been applied
successfully in the past \citep{Folino03cellular,Alba02Parallelism}.
However, in the case of MOEAs, these
approaches \citep{Luna15Survey} need to deal with the whole solution set, the PF.
 This imply to use different distribution
and sharing mechanisms, as there exist a tension between the speedup
achievable from parallelization and the need to globally recombine the
results to accurately identify the PF
\citep{Branke04Parallelizingcone}.

MOPs usually require a high number of variables, meaning that the MOEAs need to deal with large individuals and spent significant extra time for crossover, mutation and migration. Different authors have proposed methods to divide the decision space (the chromosome) to improve the performance and solution quality. In this aspect, the co-evolution model is a dimension-distributed model where a high-dimensional problem is divided into lower dimensional problems \citep{Gong15models,Tonda12cooperative}, and evolved separately. One example of application of this technique was described in \citep{Kimovski15Parallel}. The method presented in that works involves different workers that evolve sub-populations created and recombined by a master process, which performs different recombination alternatives from the parts returned by worker processes. A high dimensional problem was used to compare these
alternatives. In \citep{Dorronsoro13superlinear}, a distributed
coevolutionary island model was used.  Although in both papers
significant speedups were attained, only a low number of nodes were
employed (8). However, when the number of islands is increased, the division
of each section of the chromosome becomes smaller, and the scalability
may be affected by obtaining lower quality solutions in the same
amount of time.

%5 WE HAVE PROPOSED HPMOON

@@

%6 IN THIS PAPER WE WILL BE PROVING

@@
